Research Proposal Template

### 2019-11-03 _support/foothead/repage/repage_response_referee.tex

\documentclass[12pt,english]{article}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage{listings}
\usepackage{csquotes}

% url package
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue]{hyperref}

% Titling and Autho
\begin{document}

\begingroup
  \centering
  \LARGE Repage Document add Responses to Referees to End of File \\[1.5em]
  \large \href{http://fanwangecon.github.io/}{Fan Wang} (\href{http://fanwangecon.github.io/Tex4Econ}{Tex4Econ}) \\[1.5em]
  \large \today \par
\endgroup

\begin{abstract}
We paginate the main body of the file, re-paginate appendix with letter section headings, then re-paginate a post appendix section with numeric section headings. Final section could be appended file response to referees, which is included with main file to allow for consistent table and graph referencing and citations, but then should be split out as separate file afterwards.
\end{abstract}

\section{Introduction}

\paragraph{Searchs}
\begin{itemize}
  \item latex reset page number
\end{itemize}

\paragraph{Code} Core Latex

\begin{lstlisting}
  % Reset Appendix
  \pagenumbering{arabic}
  \setcounter{page}{1}
  % Reset Response to Referee
  \setcounter{section}{0}
  \renewcommand{\thesection}{\arabic{section}}
\end{lstlisting}

\paragraph{Links}
\begin{enumerate}
  \item \href{https://tex.stackexchange.com/questions/259085/restart-page-numbering-for-memoir-appendix}{Restart page numbering for memoir appendix}
\end{enumerate}

\section{Data\label{sec:data}}
\Blindtext
\section{Estimation\label{sec:esti}}
\Blindtext
\section{Conclusion}
\blindtext

\pagebreak
\clearpage

\appendix

\pagenumbering{arabic}
\setcounter{page}{1}

\section{Data Details\label{app:data}}
\blindtext
\section{Derivations}
\blindtext
\section{Robustness Checks}
\Blindtext
\pagebreak
\clearpage

\setcounter{section}{0}
\renewcommand{\thesection}{\arabic{section}}

\section{Responses to Editor}
\begin{quotation}
\textbf{AE: }\enquote{\blindtext}
\end{quotation}

In Sections \ref{sec:data} and \ref{app:data}. \blindtext

\subsection{Editor Question One}
\begin{quotation}
\textbf{AE: }\enquote{\blindtext}
\end{quotation}

\blindtext
\clearpage
\pagebreak

\section{Responses to Referee One}
\begin{quotation}
\textbf{R1: }\enquote{\blindtext}
\end{quotation}

\blindtext

\subsection{Referee One Question One}
\begin{quotation}
\textbf{R1: }\enquote{\blindtext}
\end{quotation}

\Blindtext

\subsection{Referee One Question Two}
\begin{quotation}
\textbf{R1: }\enquote{\blindtext}
\end{quotation}

\Blindtext

\end{document}

\end{document}

### 2019-11-07 template/fantemplate_basic_roman/draft.tex
roman 12 double space template tex

\begin{document}

\title{Overleaf Package Template File}

@@

\maketitle
\begin{abstract}
\singlespacing \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{We estimate} the impact of educational infrastructure consolidation on educational attainment using the case of China’s rural primary school closure policies in the early 2000s. The rationale for consolidation policies is that economies of scale will enable higher quality education, but distance to school increases for children in villages with school closures. We use data from a large household survey covering 728 villages in 7 provinces in China, and exploit variation in villages’ year of school closure and children’s ages at closure to identify the causal impact of school closure. For children exposed to closure during their primary school ages, we find an average decrease of 0.60 years of schooling for girls after age 15, but no significant effect for boys. Negative effects strengthen with time since closure. There is no evidence of a differential trend in educational attainment between individuals in villages with school closure and those in villages without, as indicated by an analysis using older cohorts beyond primary school age when closure occurred. Different effects by gender may be related to greater sensitivity of girls’ enrollment to distance and greater responsiveness of boys’ enrollment to quality.\end{abstract}
\vfill
\pagebreak{}

\section{Introduction}

@@

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Data}}

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3167023}{Model}\label{sec:data}}

@@

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3140132}{Estimation}}

@@

\section{Results}

\input{"tab/tab3_fm_pna_texbody"}

@@

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3316939}{Conclusion}}

In solving and estimating this model, I developed a set of solution and estimation algorithms. The solution algorithm captures the impacts of variations in the four fixed costs, three interest rates, and one collateral constraint on the household-specific feasible risky and safe asset choice sets, the average costs (returns) of borrowing (savings) across the seven credit market participation categories, and conditional and marginal asset distributions. The estimation algorithm chooses initial values for estimation by exploring the global properties of the estimation objective function through polynomial approximations. The solution and estimation algorithms can reduce estimation time by taking advantage of scalable cloud computing resources.

>>>>

\begin{document}\fontsize{12}{14}\rm

\title{Research Proposal Template}

@@

\maketitle

@@

\section{\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3167023}{Research Design}\label{sec:design}}

@@

@@

\section{Literature and Relevance}

\section{Feasibility and Local Support}

@@
